On the Gravitational stability of gravito-turbulent accretion disks

### 2016-01-26 paper/results2d.tex
updating figs, need to correct 3d beta results, need to re-comp bg if Q depends on alpha

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 1.5cm 0.4cm
    0.0cm]{figures/viscsg_modes}\\
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0cm 0.4cm
    0.0cm]{figures/viscsg_modes_theta0d3}
  \caption{Growth rates for the 2D viscous problem as a function of
    the radial wavenumber $k$ for a range of cooling times
    $\beta$. The dashed and dotted lines correspond to asympototic
    behaviors for small and large $k$, respectively, computed from
    Eq. \ref{gammie_smallk} and \ref{gammie_bigk}. Top: without
    irradiation, bottom: partially irradiated disk. 
    \label{gammie_rate_plot}}
\end{figure}

@@

%{\bf maybe move following to discussion}
Numerical simulations of gravito-turbulent disks show there is a
maximum $\alpha$ ($\sim 0.06$) that can be sustained before
fragmentation \citep{rice11}. We can interpret this result in our
linear framework. 
%We can use our case (\ref{gvisc}) to interpret this
Suppose it is possible to balance rapid cooling ($\beta\lesssim1$) 
by generating a large gravito-turbulent heating rate
($\alpha\gtrsim 1$) through a small $Q$. Fig. \ref{gammie_maxrate_plot} 
shows that such a system would be dynamically unstable with 
growth rate $s = O(\Omega)$. This is due to the direct effect of viscous 
stress promoting instability, rather than cooling. Thus, we do not expect rapidly-cooled, 
and hence highly turbulent, self-gravitating disks to persist beyond
dynamical timescales. This is consistent with previous numerical
simulations performed by \cite{lodato05}. 
%Case (\ref{gvisc}) is consistent with 
\begin{figure}
%  \includegraphics[width=\linewidth,clip=true,trim=0cm 1.5cm 0cm
%    0.0cm]{figures/result2d_fixalpha}\\
%  \includegraphics[width=\linewidth,clip=true,trim=0cm 1.5cm 0cm
%    0.0cm]{figures/result2d_fixQ}\\
  \includegraphics[width=\linewidth,clip=true,trim=0cm 1.5cm 0.cm
    0.0cm]{figures/result2d_gvisc}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0cm 0.cm
    1.0cm]{figures/result2d_gvisc_kmax}
  \caption{Growth rates (top) at the optimal wavenumber (bottom) for
    viscous GI as a function of cooling time for the
    case shown in Fig. \ref{gammie_rate_plot}. Solid lines are
    computed from the dispersion relation (Eq. \ref{thindisk}), and the dotted line is an
    estimate from Eq. \ref{gammie_maxrate_simple}. The vertical dashed
    line marks the region with $\alpha > 1$, and the vertical
    dashed-dot line marks the region with growth timescales longer
    than dynamical. 
    \label{gammie_maxrate_plot}}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 2cm 0.cm
    0.0cm]{figures/viscsg_modes}\\
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0cm 0.cm
    0.0cm]{figures/viscsg_modes_theta0d3}
  \caption{Growth rates for the 2D viscous problem as a function of
    the radial wavenumber $k$ for a range of cooling times
    $\beta$. The dashed and dotted lines correspond to asympototic
    behaviors for small and large $k$, respectively, computed from
    Eq. \ref{gammie_smallk} and \ref{gammie_bigk}. Top: without
    irradiation, bottom: partially irradiated disk. 
    \label{gammie_rate_plot}}
\end{figure}

@@

%{\bf maybe move following to discussion}
Numerical simulations of gravito-turbulent disks show there is a
maximum $\alpha$ ($\sim 0.06$) that can be sustained before
fragmentation \citep{rice11}. We can interpret this result in our
linear framework. 
%We can use our case (\ref{gvisc}) to interpret this
Suppose it is possible to balance rapid cooling ($\beta\lesssim1$) 
by generating a large gravito-turbulent heating rate
($\alpha\gtrsim 1$) through a small $Q$. Fig. \ref{gammie_maxrate_plot} 
shows that such a system would be dynamically unstable with 
growth rate $s = O(\Omega)$. This is due to the direct effect of viscous 
stress promoting instability, rather than cooling. Thus, we do not expect rapidly-cooled, 
and hence highly turbulent, self-gravitating disks to persist beyond
dynamical timescales. This is consistent with previous numerical
simulations performed by \cite{lodato05}. 
%Case (\ref{gvisc}) is consistent with 
\begin{figure}
%  \includegraphics[width=\linewidth,clip=true,trim=0cm 1.5cm 0cm
%    0.0cm]{figures/result2d_fixalpha}\\
%  \includegraphics[width=\linewidth,clip=true,trim=0cm 1.5cm 0cm
%    0.0cm]{figures/result2d_fixQ}\\
  \includegraphics[width=\linewidth,clip=true,trim=0cm 2cm 0.cm
    0.0cm]{figures/result2d_gvisc}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0cm 0.cm
    1.0cm]{figures/result2d_gvisc_kmax}
  \caption{Growth rates (top) at the optimal wavenumber (bottom) for
    viscous GI as a function of cooling time for the
    case shown in Fig. \ref{gammie_rate_plot}. Solid lines are
    computed from the dispersion relation (Eq. \ref{thindisk}), and the dotted line is an
    estimate from Eq. \ref{gammie_maxrate_simple}. The vertical dashed
    line marks the region with $\alpha > 1$, and the vertical
    dashed-dot line marks the region with growth timescales longer
    than dynamical. 
    \label{gammie_maxrate_plot}}
\end{figure}
